\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Faizan Mohammed Jamal Shaikh} \\ \vspace{1pt}
    \small 973-368-3440 $|$ \href{mailto:faizanshaikh2007304@gmail.com}{\underline{faizanshaikh2007304@gmail.com}} $|$ 
    \href{https://linkedin.com/in/fms39}{\underline{linkedin.com/in/fms39}} $|$
    \href{https://github.com/fms39-glitch}{\underline{github.com/fms39-glitch}}
\end{center}


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology}{Newark, NJ}
      {BS in Computer Science; GPA: 3.85/4.00}{Expected May 2029}
      \resumeItemListStart
        \resumeItem{\textbf{Honors:} Dean's Scholar, Albert Dorman Honors College}
        \resumeItem{\textbf{Coursework:} Data Structures \& Algorithms, Machine Learning, Data Science, Discrete Math, Linear Algebra}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Co-founder \& Developer}{Jul 2026 -- Present}
      {Thozha}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Spearheading the development of a comprehensive settlement platform for international students, streamlining housing, banking, and community integration.}
        \resumeItem{Architecting a real-time personalized dashboard to dynamically surface affordable housing listings, banking options, and visa-specific resources based on user profiles.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant}{Jan 2026 -- Present}
      {New Jersey Institute of Technology}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Developing a Clinical Ontology Evaluation Framework leveraging Python, Pandas, and REST APIs to benchmark LLMs on 400+ SNOMED CT concepts.}
        \resumeItem{Designing LLM-as-ontology-server evaluation pipelines in collaboration with a PhD researcher, utilizing Git for version control.}
      \resumeItemListEnd

    \resumeSubheading
      {IT Support Specialist (Tier 2)}{Mar 2026 -- Present}
      {New Jersey Institute of Technology}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Delivering Tier 2 technical support and hardware management for university infrastructure, collaborating with cybersecurity teams.}
        \resumeItem{Diagnosing and resolving escalated software, hardware, and network issues in a high-volume academic environment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Secure AI Interview Environment} $|$ \emph{React, Node.js, WebRTC, Anti-Cheat}}{Aug 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a secure interview environment that actively prevents cheating by blocking unauthorized AI assistants (like Claude) and external resources during assessments.}
            \resumeItem{Implementing advanced monitoring capabilities to ensure interview integrity while maintaining a seamless candidate experience.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://xyrisvision.vercel.app}{Xyris Vision}} $|$ \emph{React, Supabase, Stripe, Computer Vision}}{Jun 2026}
          \resumeItemListStart
            \resumeItem{Built a privacy-first image redaction web application in 24 hours at the NJx Hackathon, acquiring 50+ active users.}
            \resumeItem{Engineered a client-side processing architecture to scrub EXIF metadata and redact PII using computer vision, ensuring zero server-side data persistence.}
            \resumeItem{Integrated Stripe for usage-based billing and Supabase for secure backend authentication.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://squadup.qzz.io}{SquadUp}} $|$ \emph{React, Node.js, Full-Stack}}{Feb 2026 -- Jun 2026}
          \resumeItemListStart
            \resumeItem{Architected a full-stack social platform to connect students and developers for project collaboration and talent matching.}
            \resumeItem{Implemented real-time project discovery and user matching algorithms to facilitate seamless team formation.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{http://suloku.com}{Diamond Puzzle Web Game}} $|$ \emph{React, Vite, Node.js, PostgreSQL}}{Jan 2026 -- Feb 2026}
          \resumeItemListStart
            \resumeItem{Designed and deployed a full-stack puzzle game featuring leaderboards, user preferences, and high-score tracking.}
            \resumeItem{Built a production application serving global users with a responsive frontend and persistent backend data layer.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI/ML}{: LLMs, RAG, Agentic AI, Generative AI, Fine-tuning, Model Context Protocol (MCP), PyTorch} \\
     \textbf{Languages}{: Python, JavaScript, TypeScript, SQL, HTML/CSS, Java, C} \\
     \textbf{Frameworks}{: React, Node.js, Next.js, Vite, Flask, Django, TailwindCSS, Pandas, NumPy} \\
     \textbf{Tools}{: Git, Docker, REST APIs, PostgreSQL, Supabase, Stripe, Vercel, VS Code}
    }}
 \end{itemize}

 
\end{document}
